Inferring the gravitational potential of the Milky Way with a few precisely measured stars

### 2014-03-19 text/paper2/ms.tex
change step number

We leave the potential parameters ($q_1$, $q_z$, $\phi$, $\vhalo$) free to vary, along with the Lagrange point offset, $\Loffset$, and initialize an ensemble of 64 MCMC walkers by sampling from the priors summarized in Table~\ref{tbl:params}. We run the walkers for 10000 steps to burn-in, then restart the sampler starting from the final position of the burn-in phase and run for another 10000 steps. Figure~\ref{fig:trace} shows the walker positions over the 10000 inference steps for each of the five parameters. The autocorrelation time for each parameter is displayed on its corresponding panel and the horizontal lines indicate the true simulation values for the potential parameters. Figure~\ref{fig:exp1_posterior} shows projections of the posterior probability distribution for the parameters; with perfect data, the uncertainties on the potential parameters are all $<1\%$.

>>>>

We leave the potential parameters ($q_1$, $q_z$, $\phi$, $\vhalo$) free to vary, along with the Lagrange point offset, $\Loffset$, and initialize an ensemble of 64 MCMC walkers by sampling from the priors summarized in Table~\ref{tbl:params}. We run the walkers for 10000 steps to burn-in, then restart the sampler starting from the final position of the burn-in phase and run for another 5000 steps. Figure~\ref{fig:trace} shows the walker positions over the 5000 inference steps for each of the five parameters. The autocorrelation time for each parameter is displayed on its corresponding panel and the horizontal lines indicate the true simulation values for the potential parameters. Figure~\ref{fig:exp1_posterior} shows projections of the posterior probability distribution for the parameters; with perfect data, the uncertainties on the potential parameters are all $<1\%$.
